The Expected Place of the Local Group in the Cosmic Web

### 2014-08-13 paper/main.tex
typos, comentarios andrey y nelson

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The LG is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed in the LG.  
The second is a subset with additional kinematic constaints also
constrained by observations. 
We find that the pairs in the LG sample with all constraints are: (i)
preferentially   located in filaments and sheets, (ii) located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
Applied to the observed LG, there is a potential conflict between
these alignments and recent claims of an universal subhalo accretion
direction. 
This highlights the relevance of achieving a precise characterization
of the place of the LG in the cosmic web in a the cosmological context
provided by $\Lambda$CDM.

@@

The spatial and kinematic configuration of the Local Group
(LG) galaxies is rare to find in the local Universe and in cosmological
simulations. 
The LG is dominated by the two big spirals MW and M31, the next
most-luminous galaxy is M33 which is $\sim 10$ times less massive than
M31, followed by several less luminous dwarf galaxies, up to a
distance of $\sim 3$\mpc.   
The velocity vector of M31, with a low
tangential velocity is consistent to a head-on collision orbit toward
the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

Another feature of the Local group is the relatively low velocity
dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
  references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
The environment around the Local Group has density quite close to the
average density of the universe
\citep{2003ApJ...596...19K,2005AJ....129..178K}. 
In addition, the closest massive galaxy cluster, the Virgo Cluster, is
$\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.

This combination of features make LG analogues rare to
find. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters. 
A similar abundance was found by \cite{ForeroRomero2011} by comparing the
formation history of LG pairs in constrained simulations with the
results of unconstrained cosmological simulations.

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not enough to
challenge the \lcdm model.  
Another definition of LG analogues is made
by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
definitions and resulting fraction of LG analogues, all are in
agreement with a low frequency of these pairs.

To better understand the properties of the LG and how this uncommon
pair configuration fit in the cosmological context, an immediate
question arise. 
What else can we say of the LG at larger scales?

Observationally, the LG is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group. 
At this scale, there is no evident alignment of the MW-M31 orbital
plane with the local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane as shown by
Figure $3$ in \citet{2013AJ....146...69C}.

@@

This tensor is real and symmetric, which means that can be
diagonalized. 
We note its eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. 
The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. 
If
the three, two, one or zero eigenvalues are larger than this threshold
the region is classified as peak, filament, sheet or void,
respectively.

@@

The algorithm to compute the potential is grid based. 
First we interpolate the density into a cubic grid with a
Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel. 
Then we obtain the gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. 
In our case we have used a grid size on and a gaussian smoothing with
two times larger as the typical separation between the two halos in the Local Group. 
The purpose of this choice is to have both halos in the pair a common
environment. 
In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. 
The scale for the gaussian smoothing uses the same value.

@@

We also measure the alignment of the LG halos with respect to the
cosmic web defined by their eigenvectors.
To this end we characterize each LG pair by two vectors. 
The first is $\hat{n}$, the vector marking the axis along the orbital angular
momentum of the pair, normal to its orbital plane; the second is
$\hat{r}$, the vector that connects the halos in the pair which can be
related to the alignment of the radial velocities to the web.
We quantify the alignment using the absolute value of the cosinus of
the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.

@@

The LG analogues or General Sample (GS) in this paper are pairs selected in
relative isolation, and in a wide range of masses from  $M_{200c}=5
\times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
Isolation criteria includes no halos more masive than each member in
the pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
In addition we require that pairs have no Virgo-like neighbor halo
with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$
Mpc.  
We have $5480$ pairs under these general criteria. 
A full description of the selection criteria can be found in
\citet{lganalogues,sat}.

We also define two subsets of restricted samples (RS) more closely
related to the MW-M31  dynamics according to the tolerance in
additional constraints. 
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly.  
The number of pairs in each sample is $46$ and $120$ respectively,
notice we have less pairs than in \citet{lganalogues} results, since
we removed pairs which are too close at $z=0$, i.e. their virial radii
overlaps, also we removed a couple pairs that merged or change their
mass more than $20\%$ at present time since they were detected at
$z<0.1$.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig1.pdf}
\caption{Mass distribution of pairs in the different environments
for the general sample.
The shaded regions show the mass ranges of $2\sigma$ and $3\sigma$
samples.  
\label{fig:median_fraction}}
\end{center}
\end{figure}

@@

The first result we explore is the kind of environment occupied by
our LGs. 
We find that the LGs in the GS are located across all different
evironment without any strong preferences; $1/3$  are located in
sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning $1/6$ in
voids.

The situation in the $2\sigma$ and $3\sigma$ samples is very
different. 
By large the LGs in these samples are located in filaments and sheets. 
In both samples, $\sim 50\%$ of the pairs can be found in filaments
while $\sim 40\%$ are in sheets. 
These absolute numbers in each environment for each sample are
presented in Table \ref{table:web_type}.

@@

We now characterize the preferred place of the LG samples in terms of the
web overdensity, ellipticiy and anisotropy as defined in Section
\ref{sec:simulation}.

@@

Middle and right panels show web ellipciticy and absolute prolateness
dependence on mass. 
Again we notice that within the $2\sigma$ and $3\sigma$ mass range,
the average ellipciticy and prolateness does not differ significantly
from the GS expectation.
In the RS samples the pairs are located in a narrow range for
ellipticities $0.1<e<1.0$ and absolute prolateness $|p|<0.4$.

@@

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
$|\mu|<0.2$ ($>78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
($>66$ degrees angle). 
These signals do not change significantly on
different environments as has been already show in different alignment
studies with similar \citep{Libeskind2013} or identical
\citep{ForeroRomero2014} web finding techniques as ours.
In particular these trends hold for pairs in filaments and walls.
If we consider only pairs in filaments, we have that the pair orbital
angular momentum tends to be perpendicular to the filament direction,
in the case of sheets it tends to lie perpendicular to the sheet plane.

Can the increase of the alignment strenght in the different samples be
explained as a consequence of different mass dependencies as the
results in the previous section? No. 
In Figure \ref{fig:median_alignment_n} we show the median of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different mass bins.
Lines show the median $\mu$-mass relation for the three 
eigenvectors in the GS, dots represent the results for the
2$\sigma$-3$\sigma$ samples. 
Around the total mass $1.5-2.0 \times 10^{12}$ \msun in the RS
samples, the median of $\mu$ decreases as we tighten constraints
on the pairs, but not as a result of the narrowing mass selection.

@@

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
($|\mu|=0.5$) and the angles between spins and orbital angular
momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
($|\mu|=0.24$) for MW and M31 respectively
\citep{2012ApJ...753....9V}. 
Consistent with our results of no strong alignement.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web where they reside as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
have shown that the local overdensity is the dominant web property
that define the abundance and properties of halos. Other quantities
derived from the tidal tensor play a secondary role defining
properties such as its formation history.

In our case, the fact that the preferred LG total mass is around
$1-4\times 12^{12}$\Msun implies that the preferred environment are
filaments and sheets with an overdensity close to the average
value. 
Correspondignly, the values for the ellipticity and prolateness are
also well defined for the LG pairs given its correlation with the
total mass.

@@

The most interesting feature is that these alignments are
tighter as we narrow the kinematic conditions of the LG towards the
observed values. A deeper understanding requires the study of the full
formation history and coevolution with the cosmic web, a task beyond
the scope of the work presented here.

@@

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster.

\bibliographystyle{apj}
\bibliography{references}

>>>>

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constaints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
Applied to the observed LG, there is a potential conflict between
these alignments and recent claims of an universal subhalo accretion
direction. 
This highlights the relevance of achieving a precise characterization
of the place of the LG in the cosmic web in a the cosmological context
provided by $\Lambda$CDM.

@@

The spatial and kinematic configuration of the Local Group
(LG) galaxies is very uncommon in the local Universe and in cosmological
simulations. 
The LG is dominated by two big spirals: MW and M31, the next
most-luminous galaxy is M33 which is $\sim 10$ times less massive than
M31, followed by several dozen less luminous dwarf galaxies, up to a
distance of $\sim 3$\mpc.   
The velocity vector of M31, with a low
tangential velocity is consistent with a head-on collision orbit toward
the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

Another feature of the Local Group is the relatively low velocity
dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
  references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
The environment around the Local Group has density quite close to the
average density of the universe
\citep{2003ApJ...596...19K,2005AJ....129..178K}. 
In addition, the closest massive galaxy cluster, the Virgo Cluster, is
$\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.

This combination of features makes LG analogues uncommon. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters. 
A similar abundance was found by \cite{ForeroRomero2011} by comparing the
formation history of LG pairs in constrained simulations with the
results of unconstrained cosmological simulations.

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not sufficiently rare to
challenge the \lcdm model.  
Another set of criteria for LG analogues was used
by \citet{2008MNRAS.384.1459L}, but despite differences in the
definitions and resulting fraction of LG analogues, results are in
agreement with a low pairs frequency aswell.

To better understand the properties of the LG and how this uncommon
pair configuration can be explained in the cosmological context, 
an immediate question arises: 
What else can we say of the environment of the LG on larger scales?

Observationally, the LG is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group \citep{2013AJ....146...69C}.
At this scale, there is no evident alignment of the MW-M31 orbital
plane with any local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane of galaxies
as shown by Figure $3$ in \citet{2013AJ....146...69C}.

@@

This tensor is real and symmetric, which means that it can be
diagonalized. 
We denote its eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. 
The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. 
If
the three, two, one or zero eigenvalues are larger than this threshold
the region is classified as peak, filament, sheet or void,
respectively.

@@

The algorithm to compute the potential is grid based. 
First we interpolate the density into a cubic grid with a
Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel. 
Then we obtain the gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. 
In our case we have used a grid size and a gaussian smoothing with
two times larger as the typical separation between the two halos in the Local Group. 
The purpose of this choice is to have both halos in the pair a common
environment. 
In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. 
The scale for the gaussian smoothing uses the same value.

@@

We also measure the alignment of the LG halos with respect to the
cosmic web defined by their eigenvectors.
To this end we characterize each LG pair by two vectors. 
The first is $\hat{n}$, the axis along the orbital angular
momentum of the pair, normal to its orbital plane; the second is
$\hat{r}$, the vector that connects the halos in the pair which can be
related to the alignment of the radial velocities to the web.
We quantify the alignment using the absolute value of the cosinus of
the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.

@@

The LG analogues or the General Sample (GS) in this paper are pairs selected in
relative isolation, and in a wide range of masses from  $M_{200c}=5
\times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
Isolation criteria include pair members closer than $1.3$\mpc,
 and with no massive neighbors within $5$\mpc.
In addition, we require that pairs have no Virgo-like neighbor halo
with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$
Mpc.  
We have $5480$ pairs under these general criteria. 
A full description of the selection criteria can be found in
\citet{lganalogues,sat}.

We also define two subsets of restricted samples (RS) more closely
related to the MW-M31  dynamics according to the tolerance in
additional constraints. 
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly.  
The number of pairs in each sample is $46$ and $120$ respectively,
notice we have less pairs than in \citet{lganalogues}, since
we removed pairs which are too close at $z=0$, i.e. their virial radii
overlap, also we removed a couple of pairs that merged or change their
mass more than $20\%$ at present time since they were detected at
$z<0.1$.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig1.pdf}
\caption{Mass distribution of pairs in different environments
for the general sample.
The shaded regions show the $68\%$ confidence interval of the mass ranges for $2\sigma$ and $3\sigma$
samples.  
\label{fig:median_fraction}}
\end{center}
\end{figure}

@@

The first result we explore is the kind of environment occupied by
our LGs, and use as reference sample the GS where pairs are much more
relaxed in mass and kinematic constraints.
We find that the pairs in the GS are located across all different
evironment without any strong preferences; $1/3$  are located in
sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning $1/6$ in
voids.

The situation in the $2\sigma$ and $3\sigma$ samples is very
different. 
By and large the LGs in these samples are located in filaments and sheets. 
In both samples, $\sim 50\%$ of the pairs can be found in filaments
while $\sim 40\%$ are in sheets. 
These absolute numbers in each environment for each sample are
presented in Table \ref{table:web_type}.

@@

We now characterize the preferred place of the pair samples in terms of the
web overdensity, ellipticiy and anisotropy as defined in Section
\ref{sec:simulation}.

@@

Middle and right panels show web ellipticity and absolute prolateness
dependence on mass. 
Again we notice that within the $2\sigma$ and $3\sigma$ mass range,
the average ellipticity and prolateness does not differ significantly
from the GS expectation.
In the RS samples the pairs are located in a narrow range for
ellipticities $0.1<e<1.0$ and absolute prolateness $|p|<0.4$.

@@

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
$|\mu|<0.2$ ($>78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
($>66$ degrees angle). 
These signals do not change significantly on
different environments as has been already show in different alignment
studies with similar \citep{Libeskind2013} or identical
\citep{ForeroRomero2014} web finding techniques as ours.
In particular, these trends hold for pairs in filaments and walls.
If we consider only pairs in filaments, we have that the pair orbital
angular momentum tends to be perpendicular to the filament direction,
in the case of sheets it tends to lie perpendicular to the sheet plane.

Can the increase of the alignment strength in the different samples be
explained as a consequence of different mass dependencies as in the
results in the previous section? The answer is no. 
In Figure \ref{fig:median_alignment_n} we show the median of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different mass bins.
Lines show the median $\mu$-mass relation for the three 
eigenvectors in the GS, dots represent the results for the
2$\sigma$-3$\sigma$ samples. 
Around the total mass $1.5-2.0 \times 10^{12}$ \msun in the RS
samples, the median of $\mu$ decreases as we tighten constraints
on the pairs, but not as a result of the narrowing mass selection.

@@

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
($|\mu|=0.5$) and the angles between spins and orbital angular
momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
($|\mu|=0.24$) for MW and M31 respectively
\citep{2012ApJ...753....9V}. 
This is consistent with our results of no strong alignement.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web in which they reside, as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
have shown that the local overdensity is the dominant web parameter
that define the abundance and properties of halos. Other quantities
derived from the tidal tensor play a secondary role defining
properties such as its formation history.

In our case, the fact that the preferred LG total mass is around
$1-4\times 10^{12}$\Msun $\,$implies that the preferred environment are
filaments and sheets with an overdensity close to the average
value. 
Correspondignly, the values for the ellipticity and prolateness are
also well defined for the LG pairs given its correlation with the
total mass.

@@

The most interesting feature is that these alignments are
tighter as we narrow the kinematic conditions of the LG towards the
observed values. A deeper understanding requires the study of the full
formation history and coevolution with the cosmic web, a task beyond
the scope of the work presented here.
However, such alignments can be traced in observations by looking for 
similar pairs samples (or even a more unconstrained pair sample) in galaxy surveys and study the angle between
pair axis and surrounding filament computed using a filament finder, 
such as codes presented by \citet{2010MNRAS.407.1449G,2011MNRAS.414..350S}.

@@

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments.
\bibliographystyle{apj}
\bibliography{references}
